Beliefs about the development of mental life

### 2021-08-01 paper/paper.Rmd
spellcheck

What do these studies reveal about US adults' understanding of the contributions of nature vs. nurture to the development of human mental life? One consistent finding across these studies is that participants attributed many capacities to newborns, at least to a moderate degree. In addition to _bodily sensations_ and _negative affect_—obvious aspects of a newborn’s experience of the world—participants also reported that newborns had fairly substantial social-cognitive abilities, including, critically, "learning from other people". Indeed, in Study 4 participants considered biological "preprogramming" to play a rather important role in the ability to learn from other people, and to have some non-trivial impact even on the most purely cognitive ability included in that study, reasoning about things (see Figure \@ref(fig:fig03)). Rather than "intuitive empiricists" [@wang.feigenson2019], then, US adults might be better described as "intuitive constructivists" who viewed newborns as predisposed and innately equipped to learn from the people around them.

@@

Finally, we assessed which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensations*, *negative affect*, *social connection*, and *cognition and control*). We specified in our preregistration that this assessment would be conducted primarily through visualization, but to complement this visualtion we also conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs. intrinsic), domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge. Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: _lmer(response ~ mechanism type * domain + (1 + mechanism type + domain | participant) + (1 | developmental mechanism) + (1 | capacity)_. We also conducted separate, analogous regression analyses for each domain separately. In all of these analyses, mechanism type and domain were effect-coded for comparisons to the grand mean collapsing across mechanism types and domains. (Note that these analyses omitted the mechanism "the child’s brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses; see Results.)

>>>>

What do these studies reveal about US adults' understanding of the contributions of nature vs. nurture to the development of human mental life? One consistent finding across these studies is that participants attributed many capacities to newborns, at least to a moderate degree. In addition to _bodily sensations_ and _negative affect_—obvious aspects of a newborn’s experience of the world—participants also reported that newborns had fairly substantial social-cognitive abilities, including, critically, "learning from other people". Indeed, in Study 4 participants considered biological "preprogramming" to play a rather important role in the ability to learn from other people, and to have some non-trivial impact even on the most purely cognitive ability included in that study, reasoning about things (see Figure \@ref(fig:fig03)). Rather than "intuitive empiricists" [@wang.feigenson2019; @berent.etal2021], then, US adults might be better described as "intuitive constructivists" who viewed newborns as predisposed and innately equipped to learn from the people around them.

@@

Finally, we assessed which developmental mechanisms were considered to be the most or least important in the development of each of the individual mental capacities included in this study (*bodily sensations*, *negative affect*, *social connection*, and *cognition and control*). We specified in our preregistration that this assessment would be conducted primarily through visualization, but to complement this visualization we also conducted a multilevel linear regression regressing responses to this question onto type of developmental mechanism (extrinsic vs. intrinsic), domain, and an interaction between them, including the maximal random effects structure that allowed the model to converge. Using the "lme4" package for R [@bates.etal2015], we specified this model as follows: _lmer(response ~ mechanism type * domain + (1 + mechanism type + domain | participant) + (1 | developmental mechanism) + (1 | capacity)_. We also conducted separate, analogous regression analyses for each domain separately. In all of these analyses, mechanism type and domain were effect-coded for comparisons to the grand mean collapsing across mechanism types and domains. (Note that these analyses omitted the mechanism "the child’s brain changes [...]", because it was the only mechanism that was difficult to classify as either intrinsic or extrinsic via EFA and clustering analyses; see Results.)

### 2021-08-01 supplement/supplement-main.Rmd
spellcheck

As in Study 1, we examined the results of three factor retention protocols (parallel analysis, presented in the main text; minimizing BIC; and Weisman et al.’s factor retentia criteria [@weisman.etal2017a]), and our interpretation of how best to characterize our dataset was guided by the degree of consensus among these three protocols and the interpretability of the retained factors under each protocol. Here we present these three factor retention protocols separately.

>>>>

As in Study 1, we examined the results of three factor retention protocols (parallel analysis, presented in the main text; minimizing BIC; and Weisman et al.’s factor retention criteria [@weisman.etal2017a]), and our interpretation of how best to characterize our dataset was guided by the degree of consensus among these three protocols and the interpretability of the retained factors under each protocol. Here we present these three factor retention protocols separately.
